---
title: "Untitled"
author: "David Kane"
date: "8/18/2020"
output:
  pdf_document: default
  html_document: default
---


### Loading Libraries and Data

Here are the libraries needed to create **gt** and **gtsummary** tables.

```{r setup, message=FALSE}
library(tidyverse)
library(PPBDS.data)
library(gt)
```

# Presenting regression results with **gt** and **gtsummary**

There are a few ways to visualize regression results. The most basic way is using `print()`. Here is the result of a linear regression with `lm()` using `party` to model `att_end`:

```{r lm fit 1}
fit1 <- lm(att_end ~ party, data = trains)
print(fit1)
```

This gives us the info we need but doesn't look very nice. We can use **gtsummary** to create more professional visualizations. Put the regression into `tbl_regression()`:

```{r basic gtsummary table}
library(gtsummary)
tbl_regression(fit1) 
```

## Why doesn't this work?

We can making a **gt** table using a `stan_glm()` regression as well:

```{r gtsummary with stan_glm}
library(rstanarm)
library(broom.mixed)
fit2 <- stan_glm(att_end ~ party, data = trains, refresh = 0)

tbl_regression(fit2, intercept = TRUE) %>%
  as_gt() %>%
    tab_header(title = "Regression of Attitudes about Immigration", 
               subtitle = "The Effect of Party on End Attitude") %>%
    tab_source_note(md("Source: Ryan Enos, *Causal Effect of Intergroup 
                        Contact on Exclusionary Attitudes*"))
  
```



